Dynein project log

### 2016-09-24 thesis_stuff/thesis_stuff.tex
Add last measurements from PyMol.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & 21.0nm & &\\ \hline
    $L_t$ &  7nm & & 11.15nm & &\\ \hline
    $R_b$ &  & & 1.57nm & &\\ \hline
    $R_m$ &  7nm & & 7.36nm & &\\ \hline
    $R_t$ &  & & & &\\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
  \end{tabular}
\end{center}

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm\\ \hline
    $L_t$ &  7nm & & & & 11.15nm\\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm\\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm\\ \hline
    $R_t$ &  & & & & 2.16nm \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & & &\\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
  \end{tabular}
\end{center}
